formula1

### 2021-03-30 inst/formula1.Rmd
more detail

@@

```{r,maxp2017,cache=TRUE}
rm(L2017)
mL2017 <- maxp(formula1)
mL2017
dotchart(mL2017,pch=16,main='2017 Formula 1')
dotchart(log(mL2017)[1:23],pch=16,main='2017 Formula 1, log scale')
```

>>>>

**This Rmd file takes about two hours to run without cache.**

@@

```{r,maxp2017,cache=TRUE}
rm(L2017)
mL2017 <- maxp(formula1)
mL2017
mL2017 <- mL2017[-which(names(mL2017) %in% c("Resta","Button"))]
dotchart(mL2017,pch=16,main='2017 Formula 1')
dotchart(log(mL2017)[1:23],pch=16,main='2017 Formula 1, log scale')
```
